### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@d66d3a132cc144d2439e07bf1827a5dec0874916 🚀

The relationship between the underlying pathogen pool and emergence risk
is mediated by both human-wildlife interfaces (the probability of
spillover) and opportunities for onward transmission (the probability
that spillovers become epidemics). As a proxy for both, we finally
overlaid the risk component from the composite map (see above) with the
proportion of built land, as a proxy for a mix of habitat disturbance,
potential for bat synanthropy or contact with bridge hosts like
livestock (cite Rulli et al 2021 Nature Food; cite Cui et al 2019 Nature
Reviews Microbiology), and human population density and
connectivity\textsuperscript{1,20} (add: Muylaert 2022 Proc B; Hassell
2017 TREE) (fig.~\ref{fig:compound}). Accounting for these factors, most
of South America and Europe are at comparatively lower risk,
as--although densely populated--settlements tend to be in areas with
lower potential risk. Conversely, regions like Malaysia and the northern
coast of Australia have a high evolutionary risk component, but should
represent a relatively lower effective risk due to low human density.
However, southeast Asia, the Indian subcontinent, and scattered hotspots
in sub-Saharan Africa are at high risk due to the overlap between human
populations and natural opportunities for cross-species transmission of
betacoronaviruses.

>>>>

The relationship between the underlying pathogen pool and emergence risk
is mediated by both human-wildlife interfaces (the probability of
spillover) and opportunities for onward transmission (the probability
that spillovers become epidemics)\textsuperscript{1}. As a proxy for
both, we finally overlaid the risk component from the composite map (see
above) with the proportion of built land, as a proxy for a mix of
habitat disturbance, potential for bat synanthropy or contact with
bridge hosts like livestock (cite Rulli et al 2021 Nature Food; cite Cui
et al 2019 Nature Reviews Microbiology), and human population density
and connectivity\textsuperscript{1,20} (add: Muylaert 2022 Proc B;
Hassell 2017 TREE) (fig.~\ref{fig:compound}). Accounting for these
factors, most of South America and Europe are at comparatively lower
risk, as--although densely populated--settlements tend to be in areas
with lower potential risk. Conversely, regions like Malaysia and the
northern coast of Australia have a high evolutionary risk component, but
should represent a relatively lower effective risk due to low human
density. However, southeast Asia, the Indian subcontinent, and scattered
hotspots in sub-Saharan Africa are at high risk due to the overlap
between human populations and natural opportunities for cross-species
transmission of betacoronaviruses.
